\chapter{Acknowledgements}

I would like to thank Meredith Hughes for being an amazing mentor through the process of teaching me to do advanced research, all the way from the crash course in radio astronomy at the beginning of my Junior year through this thesis. I'm blessed to have worked with such a dedicated advisor who cares so much about the learning process for each and every student. Going to Hawaii to observe at the SMA and Seattle for AAS were unforgettable experiences that not many undergraduates have, but those are really just cherries on top of the incredible sundae of knowledge, experience, and wisdom that you've passed on to me. 

Thanks to Seth Redfield for selling me on the astronomy program here at Wesleyan and getting me involved with the 24$''$ observing program. I may never live down getting flung from my chair as the monkey in an angular momentum demonstration he put me up to, but at least I'm better at ultimate frisbee. 

Thanks to Kevin Flaherty, for helping me out with everything from cluster computing to statistical tests, and to Roy Kilgard, for the endless patience in helping me with computer issues and always being fun to stop by and talk to. Thanks to Angelo Ricarte for writing the foundation of the modeling code that I used in this thesis. 

To Mom and Dad, thanks for giving me multiplication problems before bed to help me fall asleep, even if you didn't always know the correct answer. I wouldn't be who I am today without your love and guidance. Mira, you're the best sister a little bro could ask for. 

To the basement crew, thanks for endless entertainment in times of drastic procrastination, playing darts, and letting me fly the baby drone around the library when that was our workspace without going crazy (RIP baby drone. Both a sorry and a damn you to the Fisk Telescope for breaking the last propellor). 

\titlespacing*{\chapter}{0pt}{*2}{*3}
