
\documentclass[11pt,modern]{aastex6}

 % Double spacing
\usepackage{setspace}
\setstretch{2}

\begin{document}


\title{AU Mic}

\author{Cail Daley}


\section{Observations}

AU Mic was observed on three dates with ALMA: 26 March 2014, 18 August 2014, and
24 June 2015. Each observation was composed of four spectral windows, and
employed ALMA's 12 m antennas and Band 7 receivers. One spectral window was
centered around the CO $J = (2-1)$ transition (230.538001 Ghz),
while the remaining three were set to detect continuum emission with
maximum bandwidths of 2 Ghz and channel spacing of 15.6 Mhz. Central frequencies
for the continuum bands are 228.5, 213.5, and 216.0 Ghz.

The 26 March data were obtained with 32 antennas, baselines ranging between
14 and 437 m; weather conditions were excellent, with $\sim$0.6 mm of precipitable
water vapor (PWV). The quasar J1924-2914 was used as a bandpass calibrator and Titan
was used to calibrate absolute flux. After these initial calibrations,
observations cycled every seven minutes between AU Mic and the quasar
J2101-2933 (phase calibration). In total, 35 minutes were
spent on source.

The 18 August utilized 35 antennas in a more extended antenna configuration
(baselines between 20 and 1268 m) to probe the small scale structure of the
disk. Weather conditions were poor: $\sim$1.6 mm PWV. The quasars J2056-4714
(bandpass calibration) and J2056-472 (absolute flux calibration) were observed
at the beginning of the observation window. For the remainder of the time block,
antennas cycled between seven-minute observations of AU Mic and brief
observations of the quasars J2101-2933 and J2057-3734 for phase calibration and
to test the quality of the gain transfer, respectively. AU Mic was observed for
35 minutes altogether.

The 24 June observation was taken to supplement the August observation, which was of
poor quality due to weather conditions. 37 antennas covered baselines between 30 and
1431 m, and weather conditions were good: $\sim$0.7 mm PWV. Bandpass and absolute flux calibrations, making use of J1924-2914 and
Titan respectively, were conducted at the beginning of the scheduled time block.
Short observations of the quasars J2056-3208 for phase calibration and
J2101-2933 to assess gain transfer quality were interspersed among
seven-minute observations of the source, which was observed for 33 minutes. The
host star flared during the last observation of AU Mic, from 04:23:38-04:29:58
UT.

Calibration, reduction, and imaging were carried out using the \texttt{CASA} and
\texttt{MIRIAD} software packages. Standard ALMA reduction scripts were applied
to the datasets: phase calibration was accomplished via water vapor radiometry
tables, and system temperature calibrations were performed to account for
variations in instrument and weather conditions. Flux and bandpass calibrations
were subsequently applied.

The authors travelled to the NRAO facility in Charlottesville, VA in October
2015 to further process the data; in particular, the trip was intended to allow
on-site correction of the 24 June flare. Tasks used to reduce the data at the
NRAO facility were all part of the \texttt{CASA} package. An elliptical gaussian
was fit to a small region around the star in the image plane of each dataset
using the task \texttt{imfit}, and the equatorial coordinates of the the
gaussian centroid were used to define the star position. Each observation was
then phase shifted using the task \texttt{fixvis} so that the the pointing
center was the same as the fit star position. The peak flux of the model
gaussian was also subtracted from the location of the star in the visibility
domain, so that only the disk remained.

The 24 June dataset required additional reduction due to the flare. While for
the other dates we were able to fit a single point source for the entire
observation to account for the stellar component, the flare required that the
dataset be split into one minute bins between 04:23:38 and 04:29:58 in order to
account for the variable flux of the host star. For each of these bins, we used
the task \texttt{uvmodelfit} to fit a point source to the long baseline
visibilities, which we subsequently subtracted from each bin in the visibility
domain. Subtracted point fluxes can be found in Table \ref{tab:flare fluxes}.

\begin{table}
\begin{deluxetable}{cr}
	\tablecaption{Subtracted point source fluxes \label{tab:flare fluxes}}
  \tablehead{
  \colhead{Time (UTC)} &
  \colhead{Point source flux ($\mu$Jy)}
  }
  \startdata
  03:45:0-04:20:00 (no flare) & $410 \pm\ \ 20$\\
	4:23:38-4:24:00 & $920 \pm 170$ \\
	4:23:38-4:24:00 & $11,460 \pm 100$ \\
	4:25:00-4:26:00 & $3590 \pm 100$ \\
	4:26:00-4:27:00 & $1580 \pm 100$ \\
	4:27:00-4:28:00 & $450 \pm 100$ \\
	4:28:00-4:29:00 & $460 \pm 100$ \\
	4:29:00-4:29:58 & $520 \pm 100$ \\
  \enddata
\end{deluxetable}
\end{table}

The June date pointing center, as defined by the gaussian fit to the star over
the entire observation timerange, was visibly offset from the surrounding disk;
this could be explained if the flare were not symmetric about the star, causing
the gaussian centroid to be offset from the true star location. The offset was
remedied by redefining the pointing center as follows. Because the star is known
to be located at the center of the disk, we can use information provided by the
brightness distribution of the disk to infer the star position. We do so by
selecting the brightest pixel on each side of the disk from the clean component
map (the \texttt{.model} file produced by \texttt{tclean}), and redefining the
star/pointing center as the mean of the two pixel positions. This yields offsets
of $(0.01'', -0.05'')$ for the March observation, $(0.01'', 0.00'')$ for the
August observation, and $(0.00'', 0.09'')$ for the June observation. Given the
good agreement between the calculated star position and the image center for the
two non-flare dates (March and August), we conclude that the `clean pixel' method
represents a viable way to accurately determine star position. We apply this
correction and redefine the image center with \texttt{fixvis}. For consistency,
we apply the phase shift to all three dates.

Due to the high proper motion of AU Mic, the coordinates of the three
observations' pointing centers differ by a not-insignificant amount. When
datasets with different pointing centers are cleaned together with
\texttt{tclean}, the pointing center of the first dataset is taken as the
pointing center of the cleaned image, and the data are combined in in the $uv$
plane with each subsequent dataset offset from the first as given by the coordinates
of its pointing center. In the case of AU Mic, this leads to an  image of the
disk composed of three observations offset with respect to each other. To remedy
this, we use the task \texttt{concat}, which combines datasets with their
pointing centers aligned so long as the pointing centers do not differ by more
than the value of \texttt{dirtol}. We set \texttt{dirtol} to $ 2''$, a value
larger than  AU Mic's proper motion over ALMA's $\sim 1$ year observation
baselines, to ensure the pointing centers of the three observations are aligned.


% \begin{deluxetable}{lr}	
% 	\tablecaption{Subtracted point-source fluxes \label{tab:flare fluxes}}
%   \tablehead{
%   \colhead{Time (UTC)} &
%   \colhead{Point-source Flux ($\mu$Jy)}
%   }
%   \startdata
%   03:45:0-04:20:0 (no flare) & ($4.1 \pm 0.2)  \times 10^2$\\
% 	4:23:38-4:24:00 & $(9.2 \pm 1.7) \times 10^2$ \\
% 	4:23:38-4:24:00 & $(1.146 \pm 0.010) \times 10^4$ \\
% 	4:25:00-4:26:00 & $(3.59 \pm 0.10) \times 10^3$ \\
% 	4:26:00-4:27:00 & $(1.58 \pm 0.10) \times 10^3$ \\
% 	4:27:00-4:28:00 & $(4.50 \pm 1.0) \times 10^2$ \\
% 	4:28:00-4:29:00 & $(4.60 \pm 1.0) \times 10^2$ \\
% 	4:29:00-4:29:58 & $(5.20 \pm 1.0) \times 10^2$\\
%   \enddata
% \end{deluxetable}
% \clearpage

% \clearpage
% \bibliographystyle{aasjournal}
% \bibliography{AGN_Feedback_Paper}


\end{document}
